---
title: "**Overview Table of CR models using Copulas**"
output:
  html_document:
    toc: no
    css: style.css
    code_download: true
    theme: simplex
    highlight: pygments
    toc_float:
      collapsed: no
    self_contained: false
link-citations: yes
classoption: fleqn
#runtime: shiny
fontsize: 11pt
header-includes:
- \usepackage{amsmath,url,hyperref,amsthm,amssymb}
- \usepackage{float} \floatplacement{figure}{H}
- \setlength{\headsep}{0.2in}
- \sloppy
linestretch: 0.9
---

<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
library(styler)
library(pander)
library(tidyverse)


knitr::opts_chunk$set(echo=FALSE,eval=TRUE,warning=FALSE,message=FALSE,prompt=TRUE,strip.white=TRUE,
cache=FALSE,size='tiny',comment='',fig.width=8,fig.height=4.5,options(width = 70))
```

## Introduction

This table has been created as part of the manuscript: **Competing risk models using copulas: A comprehensive review** with the aim of consolidating articles that has covered CR models using copulas. The provision of open-source and well-documented software is essential to ensure the widespread adoption of new statistical methods. Reproducibility is crucial in the development and evaluation of new methods. The table provides such details, and was constructed using R package: *reactable* (Lin, 2023).

## Explanation of the table columns

Explanation of table columns:
+ **Author(s)** author(s) of the article
+ **title** title of the article
+ **truncation** type of truncation
+ **censoring** type of censoring
+ **estimation** type of estimation use, `ML` - maximum likelihood, `CG` - copula graphics, `Bayesian`, `Cox` - Cox regression
+ **domain** Field of study `Survival`, `Actuarial`, `Econometrics`, `Social sciences`, `Hydrology`, `Reliability`, or `Others`
+ **Copula_type** copula type, including `Arch` - if Archimidean is used in general,  `Gaus` - Gaussian, `FGM` - Farlie–Gumbel–Morgenstern,  `AMH` - Ali-Mikhail-Haq, `Symm` - Symmetric copulas
+ **covariates** whether covariates are used or not
+ **code** availability of code used to generate results
+ **authors** name of author(s) (hidden)
+ **year** year the article was published (hidden)
+ **paper url** link to the paper (hidden)
+ **dataset** Whether real dataset(s) were utilised (hidden)
+ **simulation** Whether simulation study was utilised (hidden)
+ **CR type** type of CR: `CR` - for latent CR type; `CR-Obs` - Observable quantities type of CR; `semi-CR` - latent type CR in which a non-terminal event ca be censored by a terminal event, and `Cens` - dependent censoring type.

\noindent \textbf{Note:} **Visible** columns are displayed in the interactive table interface. **Hidden** columns are not displayed by default. Columns can be filtered, arranged in ascending/descending order. Entries can be searched in the interactive table and it contains 181 articles on competing risks models using copulas.

## Table of reviewed articles
```{r}
library(reactable)
library(htmltools)

data <- read.csv2("./table.csv", header = TRUE, sep = ";")

# Add new papers published after June 30, 2024
new_rows <- data.frame(
  authors = c("Gelis-Cadena K, Daniels M, Siddique J", "Crommen G, Deresa NW, D’Haen M, Ding J, Willems I, Van Keilegom I"),
  year = c(2025, 2025),
  title = c("A Bayesian Nonparametric Approach for Semi-Competing Risks with Application to Cardiovascular Health", "Recent advances in copula-based methods for dependent censoring"),
  paper = c("https://arxiv.org/pdf/2506.20860", "https://www.idescat.cat/sort/sort491/49.1.1.Crommen-etal.pdf"),
  model = c("non", "several"),
  truncation = c("", "left"),
  censoring = c("right", "right"),
  field = c("Survival", "Survival"),
  type = c("D-vine Gaussian", "Arch Gaussian"),
  type_covariates = c("yes", "yes"),
  code = c("no", "yes"),
  datasets = c("yes", "yes"),
  simulation = c("no", "yes"),
  CR_type = c("semi-CR", "Cens")
)

data <- rbind(data, new_rows)

# Create a reactable table
htmltools::browsable(
  tagList(
    tags$button(
      "Show/hide more columns",
      onclick = "Reactable.setHiddenColumns('cr-table', prevColumns => {
        return prevColumns.length === 0 ? ['type_covariates', 'paper', 'datasets', 'authors', 'CR_type'] : []
    })"
),
reactable(
  data,
  filterable = TRUE,
  resizable = TRUE,
  bordered = TRUE,
  highlight = TRUE,
  striped = TRUE,
  compact = TRUE,
  wrap = FALSE,
  selection = "multiple", 
  onClick = "expand",
  searchable = TRUE,
  showSortable = TRUE,
  pageSizeOptions = c(5,10,20,30),
 # rownames = TRUE,
  pagination = TRUE,
  defaultPageSize = 10,
  showPageSizeOptions = TRUE,
  paginationType = "jump",
  columns = list(
    title = colDef(name = "Title",cell = function(value, index) {
    # Render as a link
    url <- data[index,"paper"]
    htmltools::tags$a(href = url, target = "_blank",data[index,"title"])
  }, minWidth = 300, sticky = "left"),
    truncation = colDef(name = "Truncation", show = FALSE),
    censoring = colDef(name = "Censoring"),
    model = colDef(name = "Model", minWidth = 70),
    field = colDef(name = "Field", minWidth = 65),
    type = colDef(name = "Type"),
    type_covariates = colDef(name = "Covariates", show = FALSE, cell = function(value) {
    if (value == "no") "\u274c no" else "\u2714\ufe0f yes"}),
    code = colDef(name = "Code",cell = function(value, index) {
        if (value == "no") {
          "\u274c not accessible"
        } else {
          url <- data[index, "code"]
          htmltools::tags$a(href = url, target = "_blank", data[index, "code"])
        }
      }),
    authors = colDef(name = "Authors",show = FALSE),
    year = colDef(name = "Year", minWidth = 55),
    paper = colDef(name = "Paper",cell = function(value, index) {
    url <- data[index,"paper"]
    htmltools::tags$a(href = url, target = "_blank",data[index,"paper"])},show = FALSE),
    datasets = colDef(name = "Datasets", minWidth = 80, cell = function(value) {
    if (value == "no") "\u274c no" else "\u2714\ufe0f yes"}),
    CR_type = colDef(name = "CR type",show = FALSE),
    simulation = colDef(name = "Simulation",cell = function(value) {
    if (value == "no") "\u274c no" else "\u2714\ufe0f yes"},show = FALSE)
  ),
      elementId = "cr-table"
)
))
```








