---
title: "**Overview Table of CR models using Copulas**"
output:
  html_document:
    toc: no
    css: style.css
    code_download: true
    theme: simplex
    highlight: pygments
    toc_float:
      collapsed: no
    self_contained: false
link-citations: yes
classoption: fleqn
#runtime: shiny
fontsize: 11pt
header-includes:
- \usepackage{amsmath,url,hyperref,amsthm,amssymb}
- \usepackage{float} \floatplacement{figure}{H}
- \setlength{\headsep}{0.2in}
- \sloppy
linestretch: 0.9
---

<style>
body {
text-align: justify}
</style>

```{r setup, include=FALSE}
library(styler)
library(pander)
library(tidyverse)


knitr::opts_chunk$set(echo=FALSE,eval=TRUE,warning=FALSE,message=FALSE,prompt=TRUE,strip.white=TRUE,
cache=FALSE,size='tiny',comment='',fig.width=8,fig.height=4.5,options(width = 70))
```

## Introduction

This table has been created as part of the manuscript: **Competing risk models using copulas: A comprehensive review** with the aim of consolidating articles that has covered CR models using copulas. The table provides such details, and was constructed using R package: *reactable* (Lin, 2023).

## Explanation of the table columns
Explanation of table columns:

+ **Title** title of the article
+ **Truncation** type of truncation
+ **Censoring** type of censoring
+ **Estimation** type of estimation use, `ML` - maximum likelihood, `CG` - copula graphics, `Bayesian`, `Cox` - Cox regression
+ **Domain** Field of study `Survival`, `Actuarial`, `Econometrics`, `Social sciences`, `Hydrology`, `Reliability`, or `Others`
+ **Copula_type** copula type, including `Arch` - if Archimidean is used in general,  `Gaus` - Gaussian, `FGM` - Farlie–Gumbel–Morgenstern,  `AMH` - Ali-Mikhail-Haq, `Symm` - Symmetric copulas
+ **Covariates** whether covariates are used or not
+ **Code** availability of code used to generate results
+ **Author(s)** name of author(s) (hidden)
+ **Year** year the article was published (hidden)
+ **Paper url** link to the paper (hidden)
+ **Dataset** Whether real dataset(s) were utilised (hidden)
+ **Simulation** Whether simulation study was utilised (hidden)
+ **CR type** type of CR: `CR` - for latent CR type; `CR-Obs` - Observable quantities type of CR; `semi-CR` - latent type CR in which a non-terminal event ca be censored by a terminal event, and `Cens` - dependent censoring type.

\noindent \textbf{Note:} **Visible** columns are displayed in the interactive table interface. **Hidden** columns are not displayed by default. Columns can be filtered, arranged in ascending/descending order. Entries can be searched in the interactive table and it contains 181 articles on competing risks models using copulas.

## Table of reviewed articles
```{r}
library(reactable)
library(htmltools)

data <- read.csv2("./table.csv", header = TRUE, sep = ";")

# Create a reactable table
htmltools::browsable(
  tagList(
    tags$button(
      "Show/hide more columns",
      onclick = "Reactable.setHiddenColumns('cr-table', prevColumns => {
        return prevColumns.length === 0 ? ['type_covariates', 'paper', 'datasets', 'authors', 'CR_type'] : []
    })"
),
reactable(
  data,
  filterable = TRUE,
  resizable = TRUE,
  bordered = TRUE,
  highlight = TRUE,
  striped = TRUE,
  compact = TRUE,
  wrap = FALSE,
  selection = "multiple", 
  onClick = "expand",
  searchable = TRUE,
  showSortable = TRUE,
  pageSizeOptions = c(5,10,20,30),
 # rownames = TRUE,
  pagination = TRUE,
  defaultPageSize = 10,
  showPageSizeOptions = TRUE,
  paginationType = "jump",
  columns = list(
    title = colDef(name = "Title",cell = function(value, index) {
    # Render as a link
    url <- data[index,"paper"]
    htmltools::tags$a(href = url, target = "_blank",data[index,"title"])
  }, minWidth = 300, sticky = "left"),
    truncation = colDef(name = "Truncation", show = FALSE),
    censoring = colDef(name = "Censoring"),
    model = colDef(name = "Estimation", minWidth = 70),
    field = colDef(name = "Domain", minWidth = 65),
    type = colDef(name = "Copula_ype"),
    type_covariates = colDef(name = "Covariates", show = FALSE, cell = function(value) {
    if (value == "no") "\u274c no" else "\u2714\ufe0f yes"}),
    code = colDef(name = "Code",cell = function(value, index) {
        if (value == "no") {
          "\u274c not accessible"
        } else {
          url <- data[index, "code"]
          htmltools::tags$a(href = url, target = "_blank", data[index, "code"])
        }
      }),
    authors = colDef(name = "Author(s)",show = FALSE),
    year = colDef(name = "Year", minWidth = 55),
    paper = colDef(name = "Paper url",cell = function(value, index) {
    url <- data[index,"paper"]
    htmltools::tags$a(href = url, target = "_blank",data[index,"paper"])},show = FALSE),
    datasets = colDef(name = "Datasets", minWidth = 80, cell = function(value) {
    if (value == "no") "\u274c no" else "\u2714\ufe0f yes"}),
    CR_type = colDef(name = "CR type",show = FALSE),
    simulation = colDef(name = "Simulation",cell = function(value) {
    if (value == "no") "\u274c no" else "\u2714\ufe0f yes"},show = FALSE)
  ),
      elementId = "cr-table"
)
))
```


